The brightness and spatial distributions of terrestrial radio sources

### 2013-07-16 articles/Article-RFI-distribution/article-rfi-distribution.tex
Submitted final version

%\usepackage[colorlinks=true,linkcolor=customlinkcolor,urlcolor=customlinkcolor,citecolor=customcitecolor,pdftex]{hyperref}
\usepackage[pdftex]{hyperref}

@@

It is common knowledge that in a uniform Euclidian Universe source counts behave like power-law distributions. The differential distribution for sources on a flat surface is a power law with -2 exponent. We will derive this expected intrinsic source distribution for interfering radio sources. After that, we will analyse the issues that arise when measuring the distribution by counting samples.

>>>>

\usepackage[colorlinks=true,linkcolor=customlinkcolor,urlcolor=customlinkcolor,citecolor=customcitecolor,pdftex]{hyperref}
%\usepackage[pdftex]{hyperref}

@@

It is common knowledge that in a uniform Euclidian Universe source counts behave like power-law distributions. The differential source-count distribution for sources on a flat surface is a power law with -2 exponent. We will derive this expected intrinsic source distribution for interfering radio sources. After that, we will analyse the issues that arise when measuring the distribution by counting samples.
